\documentclass{article}
\usepackage[left=1.5cm, right=1.5cm, top=1.5cm, bottom=2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm,stmaryrd,amssymb,bbm,amsfonts,amstext,graphicx,multicol,array}
\usepackage{subfigure}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{indentfirst}
\usepackage{caption}
\usepackage{pdfpages}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{float}
\usepackage{booktabs}
\usepackage{graphics, graphicx}
\usepackage{booktabs}
\usepackage{adjustbox}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\setlength{\parindent}{2em}
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1.5}

\title{Literature
}
\author{Adrien Foutelet}
\date{\today}

\begin{document}

\maketitle

\section{ECON2340 Labor Economics II}

\subsection{The canonical model of skill differentials}

\subsection{Skills, tasks, and technologies}

\subsection{Superstars and Mediocrities}

\subsection{Comparative advantage, self-selection, and the Roy model}

\subsubsection{Borjas, George J. “Self-Selection and the Earnings of Immigrants.” The American Economic
Review, vol. 77, no. 4, 1987, pp. 531–53.}

Research question: How are the earnings of the immigrant population compared to those of the native population affected by the endogeneity of the decision to migrate?



\subsubsection{Chandra, Amitabh, and Douglas O. Staiger. ”Productivity Spillovers in Health Care: Evidence
from the Treatment of Heart Attacks.” Journal of Political Economy 115.1 (2007): 103-140.}

\subsubsection{Kirkeboen, Lars J., Edwin Leuven, and Magne Mogstad. ”Field of Study, Earnings, and
Self-Selection.” The Quarterly Journal of Economics 131.3 (2016): 1057-1111.}

\subsubsection{Hanson, Gordon, and Chen Liu. ”Immigration and occupational comparative advantage.”
Journal of International Economics 145 (2023): 103809.}




\begin{thebibliography}{9}

\bibitem{chodorow2024}
G. Chodorow-Reich, M. Smith, O. Zidar, E. Zwick. Tax Policy and Investment in a Global Economy. Working Paper, 2024.

\end{thebibliography}

\end{document}